### 2024-07-26 Scripts/Manuscript/manuscript.Rmd
minor technical corrections

keywords          : "reliability, validity, measurement, reporting, replicability, credibility, psychology"
wordcount         : "203"

@@

This manuscript was created in RStudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/>.

@@

[^2]: For 7 measures the number of items were modified from the original article to the replication. To check whether or not this had a confounding impact on our results, we re-ran the analyses testing the hypotheses excluding data from these studies. We found that removing these measures' data had minimal impact on the overall results. Therefore, the results presented below were based on data from all the measures.

Because of this multilevel structure we initially planned to conduct multilevel models alongside our single-level regression models for testing Hypothesis 3, 5, and 6. However, these analyses were omitted, because group sizes were small. The results from these analyses are reported in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.Rmd)) for the sake of completeness and transparency.

@@

```{r ReorderPlot23Data}
# data re-ordering (factor order was not saved in export)
plot_23_data_alpha_reordered <- data_prep_plot_23_alpha(plot_23_data_alpha)
```

>>>>

keywords          : "reliability, validity, measurement, reporting, replicability, credibility, psychology"
wordcount         : "159"

@@

This manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*\;@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/>.

@@

[^2]: For 7 measures the number of items were modified from the original article to the replication. To check whether or not this had a confounding impact on our results, we re-ran the analyses testing the hypotheses excluding data from these studies (see [Supplementary Analyses E](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd)). We found that removing these measures' data had minimal impact on the overall results. Therefore, the results presented below were based on data from all the measures.

Because of this multilevel structure we initially planned to conduct multilevel models alongside our single-level regression models for testing Hypothesis 3, 5, and 6. However, these analyses were omitted, because group sizes were small. The results from these analyses are reported in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.Rmd) for the sake of completeness and transparency.

@@

```{r ReorderPlot23Data, warning = FALSE}
# data re-ordering (factor order was not saved in export)
plot_23_data_alpha_reordered <- data_prep_plot_23_alpha(plot_23_data_alpha)
```
